Evaluating Cloud-Optimized HDF5 for NASA’s ICESat-2 Mission

### 2025-01-16 paper.qmd
suggest rephrasing
add impact of cloud reads

Fragmentation occurs when this metadata is spread out across multiple non-contiguous chunks within the file. This results in inefficiencies when accessing or modifying data because compatible libraries need to read from multiple, scattered locations in the file. Over time, as the dataset grows and evolves, this fragmentation can compound, leading to degraded performance and increased storage overhead. In particular, operations that involve reading or writing metadata, such as opening a file, checking attributes, or modifying variables, can become slower and more resource-intensive.

>>>>

Fragmentation occurs when this metadata is spread out across multiple non-contiguous chunks within the file. This makes accessing or modifying data inefficient because the HDF library has to read from multiple, scattered locations in the file. Over time, as the dataset grows and evolves, this fragmentation can compound, leading to degraded performance and increased storage overhead. In particular, operations that involve reading or writing metadata, such as opening a file, checking attributes, or modifying variables, can become slower and more resource-intensive.  When cloud-hosted files are accessed over a network using HTTPS, multiple reads increases the time to access data.
